---
title: "HDupre_HW1_DATA624"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(ggplot2)
library(tsibble)
library(fpp3)
```

## 2.1
### GAFA
```{r}
help(gafa_stock)
head(gafa_stock)
autoplot(gafa_stock, Adj_Close) +
  labs(title = 'GAFA Adjusted Closing Price',
       y = 'Price ($)',
       x = 'Year')

```

#### The interval on the GAFA data appears to be daily but the [!] symbol when we call gafa_stock indicates that the tsibble object has no set interval.

### PBS
```{r}
head(PBS)
help(PBS)
autoplot(PBS, Scripts) +
  labs(title = 'Number of Prescriptions',
       y = 'Total',
       x = 'Year') +
  theme(legend.position='none')
```

#### The interval on the PBS data is monthly, as stated in the help documentation.

### vic_elec
```{r}
head(vic_elec)
help(vic_elec)
autoplot(vic_elec, Demand) +
  labs(title = 'Victoria Electricity Demand',
       y = 'Demand',
       x = 'Date')
```

#### The interval on the vic_elec data is half-hourly.

### pelt
```{r}
head(pelt)
help(pelt)
autoplot(pelt, Hare) +
  labs(title = 'Count of Hare Pelts',
       y = 'Pelts',
       x = 'Year')

```

#### The interval for the pelt trading record data is yearly, as indicated by the [1Y] when calling the tsibble object.


## 2.2

```{r}
my_gafa <- gafa_stock

my_gada %>%
  group_by(Symbol) %>%
  filter(Close == max(Close))

```